\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
bells and whistles

\documentclass{article}
\usepackage{fullpage}
%\usepackage{times}
\usepackage{url}
\usepackage{amsmath,amsthm,amssymb,color}
%\usepackage{multicol}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{courier}
\usepackage{listings}
%\usepackage[all]{hypcap}

@@

\let\x\cdot
\lstset{
  language=Python,
  showstringspaces=false,
  tabsize=4,
  basicstyle=\ttfamily,
  keywordstyle=\bfseries\ttfamily,
  captionpos=b
}

@@

IonMonkey has two intermediate languages. There is a ``Middle
Intermediate Representation'' (MIR) which encompasses higher-level
constructs such as lambdas, objects, and strings. A variety of
optimizations are performed, and then the code is lowered to a ``Lower
Intermediate Representation'' (LIR) used for register allocation and
code generation.

@@

\begin{figure}[ht]
\begin{center}
\begin{verbatim}
var y;
if (x < 0) {
    y = x + 2000000000;
} else {
    if (x < 1000000000) {
        y = x*2;
    } else {
        y = x - 3000000000;
    }
}
\end{verbatim}
\end{center}
\caption{Code that requires information about branches to properly analyze}
\label{fig:branch}
\end{figure}

\begin{figure}[ht]
\begin{center}
\begin{verbatim}
if (x < 0) {
    x1 = Beta(x, [INT_MIN, -1]);
    y1 = x1 + 2000000000;
} else {
    x2 = Beta(x, [0, INT_MAX]);
    if (x2 < 1000000000) {
        x3 = Beta(x2, [INT_MIN, 999999999]);
        y2 = x3*2;
    } else {
        x4 = Beta(x2, [1000000000, INT_MAX]);
        y3 = x4 - 3000000000;
    }
    y4 = Phi(y2, y3);
}
y = Phi(y1, y4);
\end{verbatim}
\end{center}
\caption{Code from Figure \ref{fig:branch}, in XSA form}
\label{fig:xsa}
\end{figure}

@@

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for inserting beta nodes},
                   label={lst:add_betas}]
def addBetaNodesToFunc(cfg):
  for b in cfg.basic_blocks():
    if b.numPredecessors() == 1 and isBranch(b.pred(0).lastInstruction()):
      test = b.pred(0).lastInstruction()
      # find whether we are the true or false branch
      direction = (b == test.trueTarget())
      if test matches ``x RELOP c'':
          r = computeRange(RELOP, c, direction)
          x_prime = b.insertFront(Beta(x, r))
          replaceDominatedUses(x, x_prime)

@@

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for propagating range information},
                   label={lst:propagate_ranges}]
def propagateRanges(graph):
    worklist = []
    for block in reversePostOrder(graph):
        for insn in block:
            insn.recomputeRange()
            if !insn.isPhi() and !insn.isBeta():
                continue
            worklist.appendAll(insn.uses())

>>>>

\documentclass{article}
\usepackage{fullpage}
%\usepackage{times}
\usepackage{url}
\usepackage{amsmath,amsthm,amssymb,color}
%\usepackage{multicol}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{courier}
\usepackage{listings}
\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
%\usepackage[all]{hypcap}

@@

\let\x\cdot
\lstset{
  language=Python,
  backgroundcolor=\color{lightgray},
  showstringspaces=false,
  tabsize=4,
  basicstyle=\ttfamily,
  keywordstyle=\bfseries\ttfamily,
  captionpos=b
}
\lstdefinelanguage{JavaScript}{
  keywords={if,else,var},
  keywordstyle=\bfseries\ttfamily,
  backgroundcolor=\color{lightgray},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/}
}

@@

IonMonkey has two intermediate languages. There is a ``Middle
Intermediate Representation'' (MIR) which encompasses higher-level
constructs such as lambdas, objects, and strings. IonMonkey performs a variety of
optimizations including global value numbering and loop invariant code motion,
and then the code is lowered to a ``Lower Intermediate Representation'' (LIR)
used for register allocation and code generation. IonMonkey currently supports
code generation for the x86, x86\_64, and ARM architectures.

@@

\begin{lstlisting}[language=Javascript,
                   caption={Code that requires information about branches to properly analyze},
                   label={fig:branch}, float=ht]
var y;
if (x < 0) {
    y = x + 2000000000;
} else {
    if (x < 1000000000) {
        y = x*2;
    } else {
        y = x - 3000000000;
    }
}
\end{lstlisting}

\begin{lstlisting}[language=Javascript,
                   caption={Code from Figure \ref{fig:branch}, in XSA form},
                   label={fig:xsa}, float=ht]
if (x < 0) {
    x1 = Beta(x, [INT_MIN, -1]);
    y1 = x1 + 2000000000;
} else {
    x2 = Beta(x, [0, INT_MAX]);
    if (x2 < 1000000000) {
        x3 = Beta(x2, [INT_MIN, 999999999]);
        y2 = x3*2;
    } else {
        x4 = Beta(x2, [1000000000, INT_MAX]);
        y3 = x4 - 3000000000;
    }
    y4 = Phi(y2, y3);
}
y = Phi(y1, y4);
\end{lstlisting}

@@

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for inserting beta nodes},
                   label={lst:add_betas}, float=ht]
def addBetaNodesToFunc(cfg):
  for b in cfg.basic_blocks():
    if b.numPredecessors() == 1 and isBranch(b.pred(0).lastInstruction()):
      test = b.pred(0).lastInstruction()
      # find whether we are the true or false branch
      direction = (b == test.trueTarget())
      if test matches ``x RELOP c'':
          r = computeRange(RELOP, c, direction)
          x_prime = b.insertFront(Beta(x, r))
          replaceDominatedUses(x, x_prime)

@@

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for propagating range information},
                   label={lst:propagate_ranges}, float=ht]
def propagateRanges(graph):
    worklist = []
    for block in reversePostOrder(graph):
        for insn in block:
            insn.recomputeRange()
            if !insn.isPhi() and !insn.isBeta():
                continue
            worklist.appendAll(insn.uses())
